### 2019-03-20 papers/journal/abstract.tex
Improvement in the Related work section and changed the TODO to the respective work
Vts dia update
added the combi. problem subsection
Abstract Update

Vesicle Traffic Systems(VTSs) are the material transport 
mechanisms among the compartments inside the biological cells.

>>>>

Vesicle Traffic Systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
%
The compartments are viewed as nodes that are labeled by their chemical identity and the transport vesicles are similarly viewed as labeled edges between the nodes.
%
Several interesting questions about VTSs translate to combinatorial search and synthesis problems. 
%
We present novel SAT, SMT and QBF based encodings of the properties over vesicle traffic systems and a tool that searches for the networks that satisfy properties that are related to transport consistency conditions using these solvers. 
%
In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.

% Vesicle Traffic Systems(VTSs) are the material transport 
% mechanisms among the compartments inside the biological cells.

### 2019-03-20 papers/journal/intro.tex
Abstract Update

A characteristic feature of eukaryotic cells is the presence of multiple internal membrane bound compartments. These compartments exchange molecules amongst themselves in small membrane bound packets called vesicles ~\cite{alberts2002molecular}.  The molecular interaction network that controls the vesicle transport system involves tens of kinds of molecules which regulate each others activities and modes of action. Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
%
The high complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the aptitude of such methods.

>>>>

A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bound compartments. These compartments exchange molecules amongst themselves in small membrane-bound packets called vesicles ~\cite{alberts2002molecular}.  The molecular interaction network that controls the vesicle transport system involves tens of kinds of molecules which regulate each others activities and modes of action. Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
%
High complexity of problems in VTS also restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the aptitude of such methods.
